\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb,amsbsy}
\usepackage{fontspec}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfig}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{fancyhdr}
\usepackage{bm}
\usepackage[unicode=true,pdfborder={0 0 0},bookmarksdepth=-1]{hyperref}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{booktabs}
\newcommand{\gauss}{\ \text{G}}
% bibliography
\usepackage[backend=biber,style=numeric,giveninits=true]{biblatex}
\addbibresource{reference.bib}

% Chinese support (XeLaTeX)
\usepackage{xeCJK}
% Windows  & macOS 自動切換字體來源
\IfFileExists{/Users/dengensheng/Developer/Latexfont/NotoSerifTC.ttf}{
    \setCJKmainfont{NotoSerifTC.ttf}[
        Path = /Users/dengensheng/Developer/Latexfont/
    ]
}{
    \setCJKmainfont{Noto Serif CJK TC}
}

\setlength{\headheight}{15pt}
\setlength{\droptitle}{-1.5cm}
\parindent=0pt
\onehalfspacing
\renewcommand{\arraystretch}{1.2}

\newtheoremstyle{mystyle}
  {6pt}{15pt}
  {}
  {}
  {\bfseries}
  {.}
  {1em}
  {}

\theoremstyle{mystyle}
\newtheorem{ex}{Example}
\newtheorem{pr}{Problem}
\newtheorem{df}{Definition}
\newtheorem{thr}{Theorem}
\newtheorem{pp}{Property}

\begin{document}

\renewcommand{\headrulewidth}{0.4pt}
\lhead{\leftmark}

\begin{center}
  \vspace*{2cm}
  \Huge \textbf{Modern Physics Experiment \\ D2 Optical Pumping}\\
  \large En-Sheng Deng, Wei-Yu Huang\\
  date: 2026.03.23、03.30、04.06\\
  \vspace{1cm}

  % 圖片說明：左為組員A，右為組員B
\end{center}

\newpage

\input{section/abstract}
\input{section/optical_pumping_principle}
\input{section/apparatus_set_up}

%---------------appendix--------------------%
%\section{Experiment Theory}
%\input{Theory/1.structure of Alkali atoms}
%\input{Theory/2.interaction in M-field}
%input{Theory/3.Photon absorption}
%\input{Theory/4.OP of Rubidium}
%\input{Theory/5.Zero field transition}
%\input{Theory/6.RF spectroscopic}
%\input{Theory/7.transient eff}

%\section{Apparatus}
%\input{Apparatus/Rubidium cell}
%\input{Apparatus/detector}
%\input{Apparatus/optics}
%\input{Apparatus/temp regulation}
%\input{Apparatus/M-field}
%\input{Apparatus/RF}

%------------------PHY----------------------%
\input{section/4a}
\input{section/4b}
\input{section/4c}
\input{section/4d}

\input{section/Q_and_A}

\section{Conclusion}
The four measurements meet the stated objectives and are mutually
consistent. From the Beer--Lambert fits (Section~1) we obtain
$\sigma_{\mathrm{exp}} = 1.766(50)\times
  10^{-16}\,\si{\meter\squared}$, which reproduces the published sample
value for this apparatus class and is reduced from the theoretical peak
$\sigma_0 \simeq 10^{-15}\,\si{\meter\squared}$ by the expected
lamp-to-atom lineshape mismatch. The dominant uncertainty is the
Table~4A-1 vapour-pressure curve, amplified at low temperature by
wall-adsorption hysteresis---the reason Run~1 (cold start) is discarded
from the best-estimate average.

Optically detected magnetic resonance (Section~\ref{sec:4b}) gives a
slope ratio $m_{87}/m_{85} = 1.554(22)$, fixing the nuclear spins as
$I_{87} = 3/2$ and $I_{85} = 5/2$ and identifying the two Zeeman dips.
Combining the isotopes in a single weighted regression yields a
sweep-coil constant
$k_{\mathrm{sweep}} = 0.6397(39)\,\si{\gauss\per\ampere}$ with a
residual ambient field
$|B_0| = 0.2263(24)\,\si{\gauss}$ along the optical axis,
cross-checked by the zero-field crossing currents
$I_{\mathrm{sweep}}^{(0)} = 0.3567(58)\,\si{\ampere}$ and $0.3575(80)\,\si{\ampere}$
shared by both isotopes. Extending to \SIrange{200}{1000}{\kilo\hertz} with the main
coils energised gives
$k_{\mathrm{main}} = 8.579(24)\,\si{\gauss\per\ampere}$ with an
intercept consistent with zero, so the two calibrations close on
themselves.

At $B \simeq \SI{7}{\gauss}$ (Section~\ref{sec:4c}) the single low-field
dip resolves into the Breit--Rabi fan: five lines for $^{87}$Rb (the
weakest $F=1,\,M{=}{-}1{\to}0$ transition falls below our detection
threshold) and all ten for $^{85}$Rb. Every matched line agrees with the
numerical Breit--Rabi prediction at the \SI{0.1}{\%} level, with
per-isotope mean residuals
$\overline{\Delta B}_{87} = \SI{-0.02}{\milli\gauss}$ and
$\overline{\Delta B}_{85} = \SI{+0.01}{\milli\gauss}$---a far stronger
test of the main-field calibration than the low-field linear-Zeeman
intercepts admit. The sign-alternating $^{85}$Rb residual pattern is
the signature of a ${\sim}1\%$ sweep-axis mis-scaling, within the
$0.6\%$ calibration uncertainty of Eq.~\ref{eq:sweep_cal} and not worth
re-fitting.

The transient measurements (Section~\ref{sec:4d}) yield an isotopic
pumping-time ratio $\tau_p^{87}/\tau_p^{85} = 1.20005(22)$ at
$V_{\mathrm{pp}} = \SI{2}{\volt}$, in $3\%$
agreement with a Franzen--Emslie rate-equation simulation ($1.164$)
whose Clebsch--Gordan-weighted absorption rates predict faster pumping
in $^{85}$Rb because its dominant $F{=}3\!\to\!F'{=}3$ channel is
stronger and its ``bottleneck'' sublevel pumps faster. The observed
Rabi-oscillation period follows the expected
$T = k/V_{\mathrm{rf}} + T_0$ scaling, though the three available
$V_{\mathrm{pp}}$ settings leave effectively one degree of freedom per
isotope; denser voltage sampling is the most useful future improvement
for this sub-experiment.

The dominant systematic limitations are therefore known and quantified:
the Table~4A-1 density curve (tens of percent over the operating range)
in Section~1, the CH3-to-$I_{\mathrm{sweep}}$ affine mapping
(${\sim}\SI{20}{\milli\gauss}$) and main-field-calibration propagation
in Section~\ref{sec:4c}, and the sparse $V_{\mathrm{pp}}$ grid in
Section~\ref{sec:4d}. Replacing the lamp-profile absorption measurement
with a narrow-linewidth laser density calibration, denser
$V_{\mathrm{pp}}$ sampling, and active temperature regulation (rather
than heater-off coast) would address each of these in turn. Within
these limits, every measurement agrees with the Breit--Rabi description
of the Rb ground state, and the full apparatus---from Helmholtz coil
geometry through ambient-field cancellation to the vapour cell
itself---is self-consistent to better than one part in $10^3$.

\section{reference}
\nocite{*}
% \printbibliography

\input{section/Appendix}
\end{document}
